Frequency of low and high mass galaxy pairs in the IllustrisTNG cosmological simulation

### 2023-06-28 paper/pears.tex
added sepcut and vircut plots, sepcut text, edited fig 3 caption

\newcommand{\mlg}{\ensuremath{M_{\rm LG}}}
\newcommand{\mmto}{\ensuremath{M_{\rm M31}}}
\newcommand{\mmw}{\ensuremath{M_{\rm MW}}}
\newcommand{\vtan}{\ensuremath{v_\textrm{tan}}}
\newcommand{\vrad}{\ensuremath{v_\textrm{rad}}}
\newcommand{\ms}[1]{\ensuremath{M_{*{#1}}}}
\newcommand{\reflabel}[1]{\ensuremath{^{\mbox{\scriptsize{#1}}}}}
\newcommand{\scsep}{\ensuremath{\rm r_{sep}/r_{vir}}}
\newcommand{\scvel}{\ensuremath{\rm v_{rel}/v_{vir}}}
\newcommand{\subcat}{\textit{Subhalo Catalog}}
\newcommand{\starcat}{\textit{Subhalo + Stellar Mass Catalog}}
\newcommand{\paircat}{\textit{Full Pair Catalog}}

@@

  \todo{Name data sets and refer to their names }
\end{abstract}

@@

    \item Also, major and minor mergers are important for different reasons, so studying them as separate systems is well motivated.
        - is major high mass vs major low mass different, etc since these two types of mass ratios lead to different things 
        - importance of mergers in high vs low mass galaxies (major mergers may be less important to SFH of Universe etc - look at sabrina's papers)
    \item Systematically understanding the underlying difference between low and high mass pairs, Projected vs. physical 3D separations/pairs Two routes of studying galaxy pairs are through observations and simulations, but simulations allow us to fully understand the 3D position and velocity of objects. 
    \item in this study, we'll be quantifying the pair fraction of low mass pairs, and self consistently comparing to the pair fraction of high mass systems
    \item In this work, we aim to characterize the pair fraction of both high and low mass galaxies, major and minor pairs, consistently as a function of time. 
\end{itemize}
cite Stierwalt for low mass pairs 4485/4490 (iso vs non iso pairs) 
Pearson Besla 2016 
Pearson Besla 2018 4485/4490
Luber Pearson Besla 
Nevin

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Methodology}\label{sec:methods}
We aim to quantify and characterize the frequency, or occurrence rate, of low mass ($\rm\ms{}=10^{9}-5\times 10^{10}\Msun$) and high mass ($\rm\ms{}=5\times10^{10}-10^{12}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time. 
To this end, we utilize the IllustrisTNG simulation to select halo pairs at each snapshot according to a strict set of selection criteria as outlined in the remainder of this section. 
In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulation utilized in this study.
Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our \subcat, to which we will 
add stellar mass information. %consist of the set of subhalos from which we will select pairs.
Sec.~\ref{sec:methods-am} outlines the abundance matching prescription used to associate dark matter subhalos with stellar masses, and the creation of the \starcat, from which we will select pairs.
Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria that we use to finally construct the \paircat. 
% Finally, Sec.~\ref{sec:pairprops} details some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios. -- Note: created new section

@@

        % explain what halos we will move forward with. 
    From the set of groups that pass the group mass cut, we create a catalog of all subhalos within each group that pass a ``current mass" threshold: the subhalo mass at the given snapshot, given by \texttt{SubhaloMass} field in the group catalogs, must be $M_h > 1\times10^{9}\Msun$.\footnote{Note that for the TNG100 hydro run, the subhalo mass is the total sum of all bound dark \textit{and} baryonic matter.}
    This lower mass threshold ensures that our halos are resolved into $>100$ particles, and thus should be robust to the SUBFIND and SUBLINK algorithms, even at the low mass end.

    The set of all subhalos at each snapshot that pass the group mass and current mass cuts constitutes our entire subhalo sample, which we call the \subcat. 
    At this stage, the \subcat{} consists of all subhalos which pass the
    group mass and current mass criteria, and contains the subhalo ID and associated FoF group number of each subhalo.
    From here, we will use further selection criteria to narrow down this large sample and to match pairs of subhalos in each group.
% End choosing halos     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    Primarily, applying an abundance matching prescription to assign stellar masses to each of the dark matter halos allows us to account for the observed spread in the SMHM relationship. 
    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large. 
    In addition, using stellar masses as calculated from abundance matching allows us to side step any simulation-dependent stellar mass effects.
    In the case of TNG100 specifically, it is known that the stellar masses of low mass galaxies are often overestimated compared to the galaxy luminosity function at the low mass end\cite{}. 
    Using an observationally-calibrated abundance matching prescription will thus lead to a more robust result for comparison with and predictions for observations. 
    Finally, utilizing an abundance matching prescription allows us to directly compare results between dark matter only and hydro simulations, since the stellar masses are assigned the same way. 
    We make brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation as well in Sec.~\ref{sec:discussion}.\kc{need to specify section once written}

        % what am prescription are we using? 
    In particular, we use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
    The~\citet{Moster2013} relationship is a function of the halo mass, evolves with redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.
    Additionally, stellar mass is defined separately for central halos (``hosts") and for infalling satellites (``subhalos"), where the first is a function of the virial mass of the halo and its redshift, $M_{vir}$ and $z$, and the second is a function of the mass and redshift at the time of infall, $M_{inf}$ and $z_{inf}$. 
    This assumes that the satellite halos are at the peak of their stellar mass before infall, and neglects the affect of star formation or stellar stripping within the host halo.

        % what do we use for the mass ~ 
    In this work, we will use the peak halo mass \Mpeak\ from the \sublink\ merger trees to calculate subhalo stellar masses. 
    \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with the peak halo mass ($M_{peak}$) than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$. 
    % separate citation for peak halo mass and stellar mass relatiosnhip for M > 1e11Msun 
    Using the peak halo mass additionally allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.

        % regarding the redshift dependence ~
    We additionally assume that the stellar mass of both the primary and secondary halo can change as a function of redshift after the secondary has entered the primary's halo and do not immediately cease star formation. 
    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that dwarfs $>1\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
    Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{saga}. 
    Thus, we calculate stellar masses for our subhalos using $M_{\rm peak}$ and the redshift of the current snapshot to calculate the stellar mass of each subhalo, and to account for the additional stellar mass that can form after infall.

    As mentioned in a footnote in Sec.~\ref{sec:methods-halos}, the total halo mass of subhalos in the hydro simulation includes the mass of both dark matter and baryonic particles. 
    In TNG100-1, the DM particle mass is decreased XX\% compared to the DM particle mass in \tng100-1 Dark to account for the additional mass of baryons, such that the total mass of the halo will remain roughly the same between the dark matter only and hydro simulations. 
    Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100-1 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run, \texttt{SubhaloMass}.

        % realizations? 
    For each subhalo at each snapshot in our full subhalo sample (see Sec.~\ref{sec:methods-halos}), we create a "realization" of the catalog for , 1000 stellar mass values from the SMHM relationship to account for the systematic uncertainty in subhalo stellar masses.
    Each realization is treated as an independent sample of galaxy stellar masses, which allows us to report realistic spreads of pair properties.
    Thus, we create 1000 separate pair catalogs, and compute pair properties (pair frequency, separations, etc) for each individual abundance matching realization.
    \kc{what is the name of this catalog? (Isolated Group cats + 1000 Stellar Mass) }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%    
% Pair selection section %
    \subsection{Pair selection}\label{sec:methods-pairs}
    The full pair sample is constructed from the set of all subhalos and their abundance matching realizations. Each pair will consist of a ``primary" more massive object, and a ``secondary" less massive companion. 
    \kc{We are starting with XX catalog, we'll sprinkle on some selection criteria, then store YY and ZZ. }

@@

    %%% 
    % begin subsubsection
    \subsubsection{Selecting primaries}
        Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their group by stellar mass. Thus, each group can have at most one primary galaxy.

        We apply mass cuts on the stellar mass of the primary to define our sample of dwarf primaries and massive primaries. Each stellar mass realization is treated independently, such that the primary of a group may change between stellar mass realizations. Additionally, some groups may not have a ``primary" in one realization, but will in others. \kc{}

        For each stellar mass realization, we rank order the subhalos of each group by stellar mass, then perform a mass cut specific to the type of group: dwarf primaries from dwarf mass groups, and massive primaries from massive mass groups (see Sec.~\ref{sec:methods-halos} for group mass criteria). 
        We define the stellar mass range for dwarf primaries and massive primaries as:
        \begin{align*} 
        \mbox{\textbf{dwarf primaries:}}&\, 1\times 10^{8}< \rm M_{*} < 5\times10^{9}\Msun \\ 
        \mbox{\textbf{massive primaries:}}&\, 5\times 10^{9}< \rm M_{*} < 1\times 10^{11}\Msun.
        \end{align*}
        \kc{justification for this stellar mass range? LG relation to put into context these ranges }
        The primary stellar mass range is chosen to replicate a set of pairs with masses similar to LMC--SMC and MW--M31. \kc{remove "pairs"}

        The stellar mass criteria is fixed, and does not change as a function of redshift. 
        The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:pairprops} for more info).

        The abundance matching prescription has a spread of $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$~\citep{Moster2013},
        \kc{move to AM section}%thus the set of selected primaries in each realization is typically unique.

        % explain special cases that people might wonder about.
        %A subhalo will not be selected as a primary if it is not the first most massive halo in the group, i.e., there are no subhalos in the group that are more massive than the primary (by stellar mass). However, s
        Since our selection is based on stellar mass, and there is a large spread in the SMHM relation, the primary for any realization of the catalog may not be the most massive subhalo in terms of total subhalo mass. 
        %This is by design, since our selection criteria are meant to more closely replicate observational pair selection criteria which use the stellar mass ratio between the primary and companion to define a major or minor pair, rather than the DM halo mass.

@@

    %%% 
    % begin secondary subsubsection
    \subsubsection{Selecting secondary companions}
        The second most massive galaxy by stellar mass in each group is then used to define the secondary companion for each primary. 
        As before, the selection of secondary companions occurs independently for each stellar mass realization, and for each snapshot, such that the population of secondaries in each realization will have a different stellar mass distribution.
        %we collect 1000 different sets of pairs for each redshift.

    \subsubsection{To create the pair catalog,}
        We create two categories of pairs: 
        major pairs and minor pairs, such that the secondary companion galaxies are selected via the stellar mass ratio between the secondary and primary.     
        % Since we have already rank ordered the halos in each stellar mass realization by their stellar mass, the stellar mass ratio will never exceed 1.   
        The stellar mass ratio criteria for major and minor pairs are:
        \begin{align*} 
        \mbox{\textbf{major pair:}}&\, \frac{1}{4}\leq \frac{\rm M_{*2}}{\rm M_{*1}}< 1 \\ 
        \mbox{\textbf{minor pair:}}&\, \frac{1}{10}\leq \frac{\rm M_{*2}}{\rm M_{*1}} < \frac{1}{4}
        \end{align*}
        \kc{give the reason for this look at z0.png}

        \kc{For each pair we store the pair separation in physical units and relative velocity. We require that each pair have a minimum separation of $15 \kpc$ between the primary and secondary, which is XX times the smoothing length of the simulation. }
        \kc{need to explain how the separations and velocities are computed from the catalog etc. }
        At smaller separations, more and more mass will be attributed to the central subhalo, which can lead to confusion in the SUBFIND catalogs. %the merger tree histories. \kc{the }.

        If a primary subhalo does not have a companion that meets the stellar mass ratio criteria, separation criteria, or lower subhalo mass criteria (see Sec.~\ref{sec:methods-halos}), the subhalo will still be considered a primary. 
        We refer to all primaries without companions as ``isolated primaries."
        \kc{move this down to the secondary section}
        If a subhalo passes the stellar mass cut for a primary, but does not have an associated companion from the selection criteria for a secondary (see next subsection), the subhalo will still be considered a primary. We refer to all primaries without companions as ``isolated primaries."
        The total set of primaries includes both paired primaries and isolated primaries.

        The pair catalog contains blah blah blah. 
        1000 sets of pairs at each snapshot blah blah

        The pair sample consists of 1000 sets of pairs at each snapshot, each set representing a different realization of the abundance matching prescription. 
        At each snapshot, we calculate the median occurrence rate and kinematic values for each of the 1000 realizations. 
        Each of the following plots shows the parameter's median and percentile spread calculated from the set of 1000 medians from each realization.

        how do we use these catalogs? Interested in the aggregate properties of the full sample, and so we will treat blah blah

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
% begin pair prop plots %  
\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{counts_1000.png}
    \caption{(Top) Median number of dwarf (left) and massive (right) primaries and pairs as a function of redshift.
    Shaded areas show the 1-99 percentile range of the median from 1000 abundance matching realizations, as described in Sec.~\ref{sec:results}.
    There are approximately 8 times as many dwarf primaries as massive primaries. 
    % dwarf galaxies
    The dwarf primary count (solid) is at a minimum at $z=4$, rises to a maximum by $z\sim1$, then decreases from $z=1\to0$. 
    The dwarf pair count (dashed) peaks at $z\sim2$.
    % Massive galaxies (right)
    The massive primary count (pink solid line in top right panel) behaves similarly to the dwarf primary count, with a minimum count at $z=4$ which rises to a maximum of $\sim2000$ halos per realization at $z\sim1$, then decreases slightly by $\sim5\%$ to $\sim$1800 halos by $z=0$. 
    Unlike dwarf pairs whose pair count peaks at $z=2$, pair count for massive galaxies (pink dashed line) follows similar behavior to the total massive primary count, with a minimum at $z=4$, and increasing to $z=\sim 1$ before leveling off. At very low redshift, the pair count and primary count have opposite behavior, with the pair count \textit{increasing} at very low redshifts of $z=0-0.25$ and \textit{peaking} at $z=0$.
    \kc{where does it peak and what is }
    (Bottom) Fraction of pairs per primary as a function of redshift (i.e., the ratio between dotted line and solid line in each column). Dwarf and massive pair fractions are roughly flat for $z=2.5-4$, but display opposite behavior for $z=0-2.5$. The dwarf pair fraction decreases steadily from $\sim0.24$ to $\sim0.08$, a decrease of roughly $65\%$, while the massive pair fraction is roughly flat between $z=1-2.5$ with an average of $0.31$, before spiking sharply from $\sim 0.29$ to $\sim 0.36$ between $z=0-0.25$, an increase of $25\%$.}
    \label{fig:counts}
\end{figure*}

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{smrdist_1000.png}
    \caption{\kc{using all 1000 realizations - combined sample of XX catalog} Stellar mass ratio distribution of all dwarf (top) and massive (bottom) pairs. Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$. Overall, the stellar mass ratio distribution of major and minor pairs of dwarf and massive galaxies show little evolution from $z=4$ (right) to $z=0$ (left). 
    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both dwarf and massive pairs.}
    \label{fig:massratio}
\end{figure*}
% end pair prop plots %  
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
% Pair prop. start %
\section{Sample: Overview of pair properties} \label{sec:pairprops}
    Utilizing the pair catalog, We compute the \# of prims in each realization of the 
    The full pair sample contains 1000 individual sets of pairs at each snapshot, for all 100 snapshots of the \tng100-1 simulation.

    Fig.~\ref{fig:counts} shows the redshift evolution of the median number of dwarf and massive primaries and pairs we identify over the redshift range $z=0-4$.   
    For each snapshot, we calculate the median number of primaries and of pairs in each realization within the Pair Catalog, yielding a set of 1000 medians. 
    The solid line and dashed lines are the median of this set of 1000 medians, and the shaded regions show the 1-99\% spread of the set.

    The number of identified primaries is smallest at $z=4$, and rises to a maximum around $z=1$ for both dwarf and massive primaries.        
    There are approximately 8 times as many dwarf primaries as massive primaries.

>>>>

\newcommand{\mlg}{\ensuremath{M_{\rm LG}}}
\newcommand{\mmto}{\ensuremath{M_{\rm M31}}}
\newcommand{\mmw}{\ensuremath{M_{\rm MW}}}
\newcommand{\vtan}{\ensuremath{v_\textrm{tan}}}
\newcommand{\vrad}{\ensuremath{v_\textrm{rad}}}
\newcommand{\ms}[1]{\ensuremath{M_{*{#1}}}}
\newcommand{\reflabel}[1]{\ensuremath{^{\mbox{\scriptsize{#1}}}}}
\newcommand{\scsep}{\ensuremath{\rm r_{sep}/r_{vir}}}
\newcommand{\scvel}{\ensuremath{\rm v_{rel}/v_{vir}}}
\newcommand{\subcat}{\textit{Subhalo Catalog}}
\newcommand{\starcat}{\textit{Subhalo + Stellar Mass Catalog}}
\newcommand{\paircat}{\textit{Full Pair Catalog}}
\newcommand{\Rvir}{\ensuremath{\rm R_{vir}}}

@@

\end{abstract}

@@

    \item Also, major and minor mergers are important for different reasons, so studying them as separate systems is well motivated.
        - is major high mass vs major low mass different, etc since these two types of mass ratios lead to different things 
        - importance of mergers in high vs low mass galaxies (major mergers may be less important to SFH of Universe etc - look at sabrina's papers)
    \item Systematically understanding the underlying difference between low and high mass pairs, Projected vs. 3D separations/pairs Two routes of studying galaxy pairs are through observations and simulations, but simulations allow us to fully understand the 3D position and velocity of objects. 
    \item in this study, we'll be quantifying the pair fraction of low mass pairs, and self consistently comparing to the pair fraction of high mass systems
    \item In this work, we aim to characterize the pair fraction of both high and low mass galaxies, major and minor pairs, consistently as a function of time. 
\end{itemize}
cite Stierwalt for low mass pairs 4485/4490 (iso vs non iso pairs) 
Pearson Besla 2016 
Pearson Besla 2018 4485/4490
Luber Pearson Besla 
Nevin

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Methodology}\label{sec:methods}
We aim to quantify and characterize the frequency, or occurrence rate, of low mass ($\rm\ms{}=10^{8}-5\times 10^{9}\Msun$) and high mass ($\rm\ms{}=5\times10^{9}-10^{11}\Msun$) galaxy pairs in cosmological simulations as a function of cosmic time. 
To this end, we utilize the IllustrisTNG simulation to select halo pairs at each snapshot according to a strict set of selection criteria as outlined in the remainder of this section. 
In Sec.~\ref{sec:methods-sims}, we provide motivation for and details of the simulation utilized in this study.
Sec.~\ref{sec:methods-halos} outlines the initial mass cuts used to define our \subcat, to which we will 
add stellar mass information. %consist of the set of subhalos from which we will select pairs.
Sec.~\ref{sec:methods-am} outlines the abundance matching prescription used to associate dark matter subhalos with stellar masses, and the creation of the \starcat, from which we will select pairs.
Sec.~\ref{sec:methods-pairs} describes the second set of selection criteria that we use to finally construct the \paircat. 
% Finally, Sec.~\ref{sec:pairprops} details some of the properties of our entire pair sample, including the total number of pairs and stellar mass ratios. -- Note: created new section

@@

        % explain what halos we will move forward with. 
    From the set of groups that pass the group mass cut, we create a catalog of all subhalos within each group that pass a ``current mass" threshold, such that the subhalo mass at the given snapshot, given by \texttt{SubhaloMass} field in the group catalogs, is
    \begin{equation*}
    \mbox{\textbf{min. subhalo mass:}}\,
    \Mhalo > 1\times10^{9}\Msun.\footnote{Note that for the TNG100 hydro run, the subhalo mass is the total sum of all bound dark \textit{and} baryonic matter.}
    \end{equation*}
    This lower mass threshold ensures that our halos are resolved into $>100$ particles, and thus should be robust to the \subfind\ and \sublink\ algorithms, even at the low mass end.  
    For each subhalo that passes both of the above criteria, we use the \sublink\ merger trees to identify the maximum subhalo mass achieved by the subhalo, \Mpeak. 
    We consider only the given snapshot and all previous snapshots in the determination of \Mpeak.

    All subhalos in a given snapshot that pass both the group and current mass selection criteria will be added to our full sample of subhalos, which we call the \subcat. 
    The catalog contains subhalos at each snapshot from $z=0-\sim4.2$ (snapshot numbers 20-99) and their associated properties, namely: Subhalo ID, FoF Group Number, current subhalo mass \Mhalo, and peak halo mass \Mpeak.
    From here, we will use further selection criteria to narrow down this large sample and to match pairs of subhalos in each group.
% End choosing halos     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    Primarily, applying an abundance matching prescription to assign stellar masses to each of the dark matter halos allows us to account for the observed spread in the SMHM relationship. 
    This is particularly important in the low mass regime ($M_h \lesssim 10^{11}\Msun$) where the scatter in the SMHM function is large, $\sim 1$dex at $M_{h}\sim 10^{10}\Msun$. 
    In addition, using stellar masses as calculated from abundance matching allows us to side step any simulation-dependent stellar mass effects.
    In the case of TNG100 specifically, stellar masses of low mass galaxies are often overestimated compared to the galaxy luminosity function at the low mass end\cite{}. 
    Using an observationally-calibrated abundance matching prescription will thus lead to a more robust result for comparison with and predictions for observations. 
    Finally, utilizing an abundance matching prescription allows us to directly compare results between dark matter only and hydro simulations, since the stellar masses are assigned the same way. 
    We make brief note of results for our equivalent analysis using the dark matter only, TNG100-Dark simulation as well in Sec.~\ref{sec:discussion}.\kc{need to specify section once written}

        % what am prescription are we using? 
    We use the abundance matching relationship presented in~\citet{Moster2013}, which provides an analytic prescription to assign stellar masses to dark matter halos. 
    The~\citet{Moster2013} relationship is a function of subhalo mass, redshift, and includes terms to account for the systematic scatter in the SMHM relationship, with larger scatter at lower halo masses.

        % realizations? 
    We elect to use the maximum subhalo mass \Mpeak\ in the stellar mass calculation, rather than the subhalo mass at the given snapshot.
    We also use the current redshift of the given snapshot, $z_{snap}$, of each subhalo in the stellar mass calculation. 
    Thus, $\ms{}=f(\Mpeak,z_{snap})$.

    Using \Mpeak\ mass allows us to remain robust to scenarios in which a secondary has formed most of its stars, then loses a significant portion of its dark matter content through tidal interactions with a primary, but retains the bulk of its stellar content.
    In fact, \citet{Munshi2021} found that the stellar mass of subhalos at $z=0$ in the ``Marvel-ous Dwarfs" and ``DC Justice League" zoom simulations are more closely correlated with $M_{peak}$ than the $z=0$ halo mass for halos with peak halo mass $10^8<M_{\rm peak}<10^{11} \Msun$.

    Using $z_{snap}$ means that we allow the stellar mass of both the primary and secondary halo to change as a function of redshift, even after the secondary has entered the primary's halo. %and do not immediately cease star formation. 
    This assumption is consistent with findings from~\cite{Akins2021}, which found that massive dwarf satellites ($M_*\approx 10^8-10^9\, \Msun$) entering MW-mass host halos are rarely quenched, and with~\cite{geha13} which finds that dwarfs $>1\Mpc$ from a MW-type galaxy are often star forming and rarely quenched.
    Additionally, the SAGA survey has found that large satellites of MW-type galaxies are often very blue, with infall into the halo spurring high rates of star formation due to the large gas fraction in dwarfs~\citep{Mao2021}. 
    % maybe need a note here on whether this is fair to extend to higher mass system?

    We then calculate the stellar mass for a given subhalo by gaussian sampling each of the fitting parameters of the analytic framework from~\cite{Moster2013}, in order to account for the spread in the SMHM relationship.
    We generate a single stellar mass ``realization" of the full \subcat\ by calculating a stellar mass for each subhalo, using an independent draw the SMHM distribution for each subhalo. 
    For each snapshot, we repeat this process 1000 times to generate 1000 realizations of stellar masses for the \subcat.
    The resulting catalog is called the \starcat, and consists of the set of all subhalos from the \subcat, as well as the 1000 stellar mass realizations. 
    Each realization is treated as an independent sample of galaxy stellar masses, which will allow us to report realistic spreads of pair properties.

    % As mentioned in a footnote in Sec.~\ref{sec:methods-halos}, the total halo mass of subhalos in the hydro simulation includes the mass of both dark matter and baryonic particles. 
    % In TNG100-1, the DM particle mass is decreased XX\% compared to the DM particle mass in \tng100-1 Dark to account for the additional mass of baryons, such that the total mass of the halo will remain roughly the same between the dark matter only and hydro simulations. 
    % Since the~\citet{Moster2013} AM relation was calibrated using DM subhalos from the \texttt{MilleniumII} dark matter only simulation, we will use the total subhalo mass from the TNG100 hydro simulation as a proxy for the corresponding DM halo mass in the TNG100-1 Dark run, \texttt{SubhaloMass}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%    
% Pair selection section %
    \subsection{Pair selection}\label{sec:methods-pairs}
    Starting from the \starcat, here we outline the pair matching process through which we generate the \paircat. 
    At each redshift, and for each stellar mass realization, we will identify subhalo pairs consisting of a "primary" and a "secondary", where primaries are the more massive of the pair by stellar mass.

@@

    %%% 
    % begin subsubsection
    \subsubsection{Selecting primaries}
        Primary galaxies (equivalently, ``primary subhalos") are the most massive galaxy of their FoF group by stellar mass, such that each group can have at most one primary galaxy.  
        Each stellar mass realization is treated independently, such that the subhalo identified as the primary of a group may change between stellar mass realizations.

        At a given snapshot, and for each stellar mass realization, we rank order the subhalos of each group by stellar mass. 
        Primaries must be the most massive subhalo in their group, and pass the following stellar mass criteria:         
        \begin{align*} 
        \mbox{\textbf{low mass primaries:}}&\, 10^{8}< \rm M_{*1} < 5\times10^{9}\Msun \\ 
        \mbox{\textbf{high mass primaries:}}&\, 5\times 10^{9}< \rm M_{*1} < 10^{11}\Msun.
        \end{align*}
        The stellar mass criteria is fixed, and does not change as a function of redshift. 
        At $z=0$, the stellar mass range for low mass primaries corresponds to isolated analogs of the LMC or M33, while the high mass primaries represent isolated analogs of the MW or M31.

        % The median number of primaries in a single stellar mass realization at $z=0$ is XX dwarf primaries and XX massive primaries (see Sec.~\ref{sec:pairprops} for more info). 
        Since our selection is based on stellar mass, and there is a large spread in the SMHM relation, a primary subhalo may not be the most massive subhalo in terms of total subhalo mass.

@@

    %%% 
    % begin secondary subsubsection
    \subsubsection{Selecting secondary companions}
        As before, the selection of secondary companions occurs independently for each stellar mass realization, and for each snapshot. 
        Secondary subhalos are defined as the second most massive subhalo in a FoF group by stellar mass. 
        Secondary subhalos with stellar mass $M_{*2}$ must have a stellar mass ratio:
        \begin{align*}
            &\mbox{\textbf{stellar mass ratio:}}\,      
            M_{*2}/M_{*1} > 1/10.
        \end{align*} 
        We do not include companions with a stellar mass ratio $M_{*2}/M_{*1} <1/10$ due to the lower bound subhalo mass criteria of $\Mhalo=10^9$, which has at least a the corresponding stellar mass of $10^6\Msun$ at $z=0$.
        The stellar mass ratio criterion ensures completeness of the sample, even at the lowest stellar masses considered.

    \subsubsection{Creating the pair catalog}
        Pairs consist of a single primary and secondary in a FoF group as selected via the criteria above. 
        Each pair is categorized as either a major or minor pair based on the stellar mass ratio between the primary and secondary. 
        The stellar mass ratio criteria for major and minor pairs are:
        \begin{align*} 
        \mbox{\textbf{major pair:}}&\, \frac{1}{4}\leq \frac{\rm M_{*2}}{\rm M_{*1}}< 1 \\ 
        \mbox{\textbf{minor pair:}}&\, \frac{1}{10}\leq \frac{\rm M_{*2}}{\rm M_{*1}} < \frac{1}{4}.
        \end{align*}

        For each pair, we calculate the physical separation (\kpc, not comoving \kpc) between the two subhalos using the \texttt{SubhaloPos} field from the group catalogs, and we require that each pair have a minimum separation of $15 \kpc$ between the primary and secondary.
        The minimum separation cut is 20 times the smoothing length of the simulation at $z=0$ which ensures that \subfind can identify the subhalos as distinct objects.

        If a primary subhalo does not have a companion that meets the stellar mass ratio criteria and separation criteria, the subhalo will still be considered a primary. 
        We refer to all primaries without companions as ``isolated primaries."
        The total number of primaries includes both isolated primaries and those with companions, and is larger than or equal to the total number of pairs.

        For each snapshot and each of the 1000 realizations of the abundance matching prescription, we create a set of isolated primaries and pairs. 
        The final \paircat is the collection of all isolated primaries and pairs at each snapshot, and includes the following information: for each isolated primary, we store the subhalo mass and stellar mass from the given realization; from each pair we store the primary and secondary subhalo masses, stellar masses, group radius, and separation.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
% begin pair prop plots %  
\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{counts_1000.png}
    \caption{(Top) Number of isolated low mass (left) and high mass (right) primaries and pairs as a function of redshift.
    The solid and dashed lines represent the median of the set of total counts from each of the 1000 stellar mass realizations in the \paircat, while the shaded regions depict the 1-99 percentile spread of the median.
    There are approximately 8 times as many low mass primaries as high mass primaries. 
    % dwarf galaxies
    The low mass primary count (left) peaks at $z=1$ (with $\sim 15000$ primary subhalos per realization), while the low mass pair count peaks at $z=2$ (with $\sim 3000$ pairs per realization). 
    % Massive galaxies (right)
    The high mass primary count (right) peaks at $z\sim1$ (with $\sim 1900$ primary subhalos per realization), while the high mass pair count peaks at $z=0$ (with $\sim 700$ pairs per realization). 
    (Bottom) Total pair fraction (fraction of primaries with a companion secondary) as a function of redshift (see Sec.~\ref{sec:pairprops} for calculation details).
    Low mass pair fraction is approximately flat between $z=2.5-4$, and decreases from $z=2.5$ to $z=0$. 
    The high mass total pair fraction is flat or decreasing from $z=1$ to $z=4$, but spikes sharply between $z=0-0.25$.}
    \label{fig:counts}
\end{figure*}

\begin{figure*}[htb]
    \centering
    \includegraphics[width=\textwidth]{smrdist_1000.png}
    \caption{Stellar mass ratio distribution of all low mass (top) and high mass (bottom) pairs for all 1000 stellar mass realizations combined. Major pairs (solid lines) are defined as pairs with mass ratio $\ms{2}/\ms{1} > 1/4$, while minor pairs (dotted lines) are defined as pairs with stellar mass ratio $1/10<\ms{2}/\ms{1}<1/4$. Overall, the stellar mass ratio distribution of major and minor pairs of low and high mass galaxies show little evolution from $z=4$ (right) to $z=0$ (left). 
    Major pairs make up $51-55\%$ of the full sample of pairs at every redshift for both low and high mass pairs.}
    \label{fig:massratio}
\end{figure*}
% end pair prop plots %  
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
% Pair prop. start %
\section{Sample: Overview of pair properties} \label{sec:pairprops}
    Utilizing the \paircat, for each snapshot, we compute the total number of primaries (isolated and paired) and pairs in each of the 1000 realizations, then take the median and 1 and 99 percentile spread on the median over all realizations. 
    Additionally, we compute the low and high mass total pair fraction (the total number of pairs, $\rm N_{pair}$, divided by the total number of primaries $\rm N_{prim}$) for each individual realization, then find the median and spread over all 1000 realizations.

    Fig.~\ref{fig:counts} shows the median number (solid and dashed lines) of identified low and high mass primaries and pairs over the redshift range $z=0-4$.   
    The shaded regions show the 1-99\% spread of the set, though the spread is hard to distinguish in the low mass case.

    The number of identified primaries is lowest at $z=4$, and rises to a maximum around $z=1$ for both low and high mass primaries.
    The median count of low mass primaries (green solid line in top left panel) reaches a maximum of $\sim15000$ halos at $z\sim0.6$, then decreases by $\sim16\%$ to 12000 halos at $z=0$. 
    The count of high mass primaries (pink solid line in top right panel) reaches a maximum of $\sim2000$ at $z\sim1$, then remains approximately constant to $z=0$. 
    There are roughly 8 times as many low mass primaries as high mass primaries.

    Unlike the primary count, the pair counts for low and high mass pairs peak at very different redshifts. 
    The count of low mass pairs (green dashed line) peaks much earlier at $z\sim2$ with $\sim3000$ pairs, and decreases to $\sim1000$ pairs at $z=0$.
    % From $z=4$ to $z=2$, the number of dwarf primaries doubles, as does the number of pairs due to the growth of structures over cosmic time.
    The pair count for high mass galaxies (pink dashed line), on the other hand, behaves more similarly to the primary count, increasing from $z=4$ to a peak at $z\sim1$, then leveling off through $z=0$.
